Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-10-25 paper/main.tex
More text on fec vs raid

\usepackage{appendix} % Fixes formatting of appendices
\usepackage[printonlyused]{acronym} % Package to handle the acronym list
\usepackage{graphicx} % We *may* use images
\graphicspath{{images/}} % and it is clean to put them in a separate dir
\usepackage{hyperref} % Internal and external links is nice
\hypersetup{pdfborder=0 0 0} % ..especially without red borders

@@

Tahoe-\ac{LAFS} uses a number of techniques to realize the functionality
demanded by a secure, distributed filesystem.

@@

When a client puts a file on the grid, it first encrypts the file, before
breaking the file into small segments. The segments are then erasure coded.
The use of \emph{erasure coding} enables Tahoe to recover a file using only a
predefined subset of the parts distributed to the storage servers, i.e. the
other nodes in the grid. Erasure coding is a type of \ac{FEC} code, which
extends a message with $C$ characters into a longer message with $N$ symbols
\cite{t_reed-solomon}.
The original $C$ characters can then be recovered from a subset of the $N$
symbols.

The properties of erasure coding can be seen up on as those of recovery in RAID
systems. \cite{t_erasure} % TODO: comparison with RAID

@@

Describe hash trees in further detail?

@@

% BibTeX bibliography lives in external file
\bibliographystyle{plain}
\bibliography{ref_sha3,ref_tahoe}

>>>>

\usepackage[numbers]{natbib}
\usepackage{appendix} % Fixes formatting of appendices
\usepackage[printonlyused]{acronym} % Package to handle the acronym list
\usepackage{graphicx} % We *may* use images
\graphicspath{{images/}} % and it is clean to put them in a separate dir
\usepackage{hyperref} % Internal and external links is nice
\hypersetup{pdfborder=0 0 0} % ..especially without red borders

@@

Tahoe-\ac{LAFS} uses a number of techniques to realize the functionality
needed by a secure, distributed filesystem.

@@

When a client puts a file on the grid, it first encrypts the file, before
breaking the file into small segments. The segments are then \emph{erasure
coded}.  The use of the Solomon-Reed erasure coding scheme, enables Tahoe to
recover a file using only a predefined subset of the parts distributed to the
storage servers, i.e. the other nodes in the grid. Erasure coding is a type of
\ac{FEC} code, which extends a message with $C$ characters into a longer message
with $N$ symbols \cite{t_reed-solomon}.  The original $C$ characters can then be
recovered from a subset of the $N$ symbols.

The properties of erasure coding can be thought of as those of parity bits in
RAID\footnote{Redundant Array of Independent Disks} systems. \citet*{t_erasure}
compare erasure coding and plain replication, and conclude that ``\emph{...
erasure codes have mean time to failures many orders of magnitude higher than
replicated systems with similar storage and bandwidth requirements.}''

@@

%TODO: Describe hash trees in further detail?

@@

% BibTeX bibliography lives in external file
\bibliographystyle{plainnat}
\bibliography{ref_sha3,ref_tahoe}
